A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-09-30 paper.tex
Rename for consistency and formatting

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{DataProvider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics are complicated in subscription services; therefore, we illustrate the challenges in this section. As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. It is notable that consumers can only initiate a refund after getting the data or in a certain time period. In this situation, the broker should host and set a vote timeline to count the votes, as well as handling the condition that not enough consumers join the vote. The process needs to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fees, which is a deal between brokers and providers. If they cannot reach a consensus on the brokerage fee during the subscription period, brokers can launch a refund and reject to handle the product. Third, the refund could be launched by providers when they fail to maintain products as committed.

>>>>

\subsection{Unsubscribe to Data Products}
When data consumers unsubscribe to data products, they are marked as not subscribing on the Product Contract, and the withdraw function is executed to pay the fee proportionally to participants, which is defined in formula~\ref{equation:unsubscribe},~\ref{equation:unsubscribe_1},~\ref{equation:unsubscribe_2}. $i$ is the number of data when refunding condition is met, $price$  is the subscription price, $M$ is the number of expected data records, $F_{b}$ (\%) is the brokerage fee which is expressed as a percentage, $F_{t}$ is the transaction fee of the smart contract, and $F_{cancel}$ is the cancellation fee charged for unsubscription. In SaaS, the cancellation fee is a way to make sure the service providers are protected if subscribers drop out at the early stage. However, asking cancellation fee arbitrarily may cause an unfair contract that leads to the legal issue, which should be carefully studied. Finally, data provider will change the encryption key to prevent unsubscribers continue accessing the following data. The new key should be updated for the remaining subscribers.
\begin{align}
    F_{Provider}(i) &= price \frac{i-1}{M} (1-F_{b}+F_{cancel}) -F_{t} \label{equation:unsubscribe} \\
    F_{Broker}(i) &= price \frac{i-1}{M} F_{b} -F_{t} \label{equation:unsubscribe_1} \\
    F_{Consumer}(i) &= price (1-\frac{i-1}{M})(1 -F_{cancel}) -F_{t} \label{equation:unsubscribe_2}
\end{align}
\subsection{Refund}
\label{section:refund}
The refund topics are complicated in subscription services; therefore, we illustrate the challenges in this section. As subscription-based services in the real-world, participants can launch a refund in the following conditions: First, consumers launch a vote for refund when the data provider does not upload data as expected after receiving the subscription fee. It is notable that consumers can only initiate a refund after getting the data or in a certain time period. In this situation, the broker should host and set a vote timeline to count the votes, as well as handling the condition that not enough consumers join the vote. The process needs to be considered carefully. Second, brokers operate the subscription platform by earning brokerage fees, which is a deal between brokers and providers. If they cannot reach a consensus on the brokerage fee during the subscription period, brokers can launch a refund and reject to handle the product. Third, the refund could be launched by providers when they fail to maintain products as committed.
